\section{Client Views}
\label{app:client-views}

The following is a list of the views planned for the client.

\subsection{General view}
This view is not for a specific action, but rather provides the frame for the rest
of the views. This view is always visible.

Should contain user log-in and client navigation.

Requirements: 10

\subsection{Create user}
A view for creating a new user (sending the proper request to the service).

Requirements: 9

\subsection{Account overview}
View the current user's account (get user info), edit user info and add credits to
the account. The overview should also show lists of all movies and songs currently
availible to the user.

Requirements: 11, 14, 24

\subsection{List movies}
\label{app:client-views-list-movies}
Display all movies. Would be nice with a show-reel of highest rated movies. Provide search
functionality in movies, as well as sorting.

Requirements: 19-20 (with \ref{app:client-views-list-songs})

\subsection{List songs}
\label{app:client-views-list-songs}
Display all songs. Show-reel of highest rated songs. Provide search functionatlity in songs,
as well as sorting.

Requirements: 19-20 (with \ref{app:client-views-list-movies})

\subsection{View movie}
\label{app:client-views-view-movie}
Show the details of a specified movie, as well as options to buy and rent the movie.

Requirements: 1-8, 15-18, 22 (with \ref{app:client-views-view-song})

\subsection{View song}
\label{app:client-views-view-song}
Show the details of a specified song, as well as the options to buy and rent it.

Requirements: 1-8, 15-18, 22 (with \ref{app:client-views-view-movie})

\subsection{Movie player}
\label{app:client-views-movie-player}
Play the specified movie.

Requirements:  21 (with \ref{app:client-views-song-player})

\subsection{Song player}
\label{app:client-views-song-player}
Play the specified song.

Requirements: 21 (with \ref{app:client-views-movie-player})

\subsection{Manager overview}
Provide functionality for uploading/creating new movies and songs (as a manager).
Provide functionality for promoting/demoting managers.

Requirements: 26-30

