\section{Email from Robert Chai}
\label{app:robertsletter}
\emph{Excerpt:}

Hi Niels,

Hope you and your team don't take it personally as my writeup is a means of
suggestions as we are trying to simplify the number of lines of code to be
written. So I do hope that the suggestion is not viewed negatively and being
opposed as a negative form of suggestion with your use of "you"repetitively
within your email.

At the end of the day, I believe though as short term we are working together
on this project.. The ideal is to work things out, be proactive on suggestions
and just work out on potential compromises along the way.

For that, I would like to first apologize to say that there were faults of mine
relying on the workings of angularjs v0.9 as my previous knowledge was based on
juz 1.5 year back while I was doing my final year project. Thank you for
sharing the link on the update of the code.

Also, i would like to thank you can your team for working with us on the
pagination segment.

Just to clarify with you, will your team be having a product logo for "moofy" or if you wouldn't have, may I partake in getting one done as the logo design would be a paramount factor for our client end web design and we would need it fast due to the unforeseen changes of not using the "RentIT" branding in the end.

Do let me know and please do reply the email to all, as I believe it would be good that everyone on the team is informed on the same page whenever an email is sent, irregardless of whether the team leaders of different end sent it, so that we need not redivert information again to the other members.

I appreciate your understanding and let's work forward to getting a great product for submission! :)

Cheers! 
Robert Chai