\subsection{Use Cases}
\label{app:usecases}
\textbf{Users:}
\begin{itemize}
\item A user must be able to login, register, and edit an account.
\item A user may deposit money into her account, to be used for later purchases.
\item A user must be able to overview movies/songs by the following categories: lexicographically, by release date, genre, rating, and popularity.
\item A user must be able to locate a specific movie/song through text search, matching movies with any property matching the text string.
\item A movie must have properties describing title of movie/song, year of release, director(s), genre(s) of movie, and a textual description.
\item A user must be able to purchase a movie/song, which will then be associated with her account.
\item A user must be able to rent a movie/song, which will then be associated with her account for 2 days.
\item A user must be able to watch any movie/song associated with her account in the browser, as long as it is still available through the service.
\item A user must be able to download any movie/song associated with her account, as long as it is still available through the service.
\item A user must be able to find all movies/songs that are or have been associated with her account, as long it is still available through the service (ie. movies the user has purchased or rented at a given time).
\item A user must be able to find all movies/songs that are associated with her account, as long it is still available through the service (ie. movies that the user can watch at the given time).
\end{itemize}
\textbf{Managers:}
\begin{itemize}
\item A manager's rights extend those of the user, so that a manager can do everything the user can, without purchase.
\item A manager must be able to upload movies/songs as well as provide properties and prices to them.
\item A manager must be able to delete movies/songs from the service.
\end{itemize}