\subsection{First Hand Impressions}
When starting the semester, even before the first lecture in the \emph{Software Development in Large Teams
with International Collaboration} course, rumors were circulating, most originating from students who had
gone through the same course the year before.

As this was the only source of information about what to expect from working with a Singaporean team, these
rumors were taken to heart and very much shaped the actual expectations of the team.

One team (from last year) was telling the story of how they had, in practice, been doing both the work they
were supposed to do and the work the Singaporean team was supposed to do. This was very much an outlier in
terms of extremity, but most rumors confirmed that expectations should be kept low, and that the Danish
team would very much have to take on a leading role in the relationship and guide the process.

It was with these expectations we went into the video conference room for the very first time to have a
virtual meeting with the Singaporean partners that we were going to work with for the following weeks.

During this first meeting, all of our expectations were seemingly proven wrong: the Singaporean team was well
prepared, and we ended up going by their agenda as they had covered all that we planned to talk about and more.

What made the greatest impression on us was that the Singaporean team had already set their sights on a
technology and researched exactly what this would mean for our common interface. They wished to develop using
AngularJS\footnote{AngularJS is a Google-developed front-end JavaScript framework. AngularJS – Superheroic
JavaScript MVW Framework, http://angularjs.org/}, and inquired as to whether it would be possible
for us to implement a RESTful\footnote{REpresentational State Transfer, a type of API based on the Hyper-Text
Transfer Protocol (HTTP), http://www.oracle.com/technetwork/articles/javase/index-137171.html} JSON\footnote{
JavaScript Object Notation, a lightweight data-interchange format based on a subset of the JavaScript
programming language, http://www.json.org/}-based interface on the server.

Leaving that meeting our expectations were through the roof: despite everything we had heard it seemed that
we had been paired with a professional, dedicated, and well-prepared group.