\section{Future improvements}
\label{sec:futureimps}
In this section we will discuss what things we would have added or improved if we were to continue working with Moofy.

\begin{description}
\item[Close account] We would like for a user to be able to close his account.
Currently the client does not support any kind of account deletion, due to lack of
time and the low priority of this requirement. The action is, however, supported in the
web service. We would like for a user to be able to close his account but open
it later with his media and funds still available to him. This should not be
too complicated to implement but due to the time restrictions on the project we
did not have time to implement it. (This would fulfill requirements 12-13,
which currently are not fulfilled.)

\item[Loading indicator] Another feature we would like to have in the future is
a loading indicator that shows when content is being loaded in the client.
Currently the user has no way of knowing if content is being loaded and may
think that something has gone wrong. A loading indicator would fix this issue
and it would be fairly simple to implement however code would have to be added
in a lot of places, and this feature was not a priority for us to get done so
we chose to focus on the report instead.

\item[Better streaming] Currently then video "streaming" is using the html
video tag utility, however this is not actually streaming the movie, it is just
a http request spiced up with some buffering and such getting the movie. Had we
had more time we would like to have added a more sophisticated method of
streaming. This would also help on the next issue as the video tag is not
supported in all browsers and different browsers support different file types,
for instance Mozilla Firefox does not support mp4 files in the video tag.

\item[Support more browsers] The current version of the client is only tested
in the most recent version of the Google Chrome browser. We would like for our
client to function in as many browsers as possible and preferably older
versions of browsers as well. This is not a requirement to the system as we
knew from the beginning that it would be extremely time consuming to identify
and deal with all cross browser compatibility issues. If the system was going
live this would however be a very important thing to fix because having a
target audience using only Google Chrome would significantly reduce the
expected revenue on Moofy.

\item[Show all current and previous files related to a user] As described in requirement
23 we would like for a user to be able to see currently available content aswell as previously
available content in one place. This is implemented in the webservice , but not yet in the
client.
\end{description}
