\section{Analysis of Project Control}
This section provides an analysis of the effects of our project control methods,
including what effect quality control and visible monitoring of progress had on
our team.

\subsection{Quality Control}
\label{sec:AnalysisQualityControl}
Having a quality plan made it easy for us to check whether a certain part of the
program meets our quality standards. Since it is the same routine for every part
of the program, it has proven, in time, to get easier and quicker to do a quality
check.

Agreeing on what we define as quality also makes it easier for each individual
group member to trust that, once a part of the program has gone through quality
checking, it is of acceptable quality, even if the quality check was done by
other group members.

In a larger project it would probably have been a good idea to have some
performance requirements, but since our project is very small, we decided that
this was not necessary and would only be a waste of time.

\subsection{Monitoring Progress}
Being able to monitor progress has proven to be very useful during our project. It
made it easy for the group to get an overview of how the project was coming along,
as well as how the work of each individual member of the group was progressing.

Given that the five of us have never worked together on a project before, there was
bound to be some difficulties when estimating tasks, and being able to monitor the
work of each group member has been a tremendous help when regulating workloads,
because it shows how much time group members put into their assigned tasks.

We are positive that monitoring progress will improve our ability to provide correct
estimates in the future, if the five of us continue to work together. So instead of
simply solving problems unbalanced workload distribution, it may, in time, prevent
them from occurring entirely.